Coherent optical creation of a single molecule

### 2020-11-25 paper.tex
Tweak figure and include beampath
Rename figure files...
Copy caption from thesis

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger ratio of Raman Rabi frequency to scattering rate.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse-time scan on resonance.
    A decaying Rabi oscillation can be observed, proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$,
    which defines the location of the atoms and molecule.
    We use a bias magnetic field $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experience predominantly $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance scales as $P$
    and follows $1/\Delta$ with an offset, where $ P$ is the power in the tweezer.
    The fit also includes a small term that is proportional to $P^2$
    which is caused by the effective magnetic field generated by the tweezer, which is perpendicular to the real magnetic field.
    (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
    and follows $1/\Delta$ with an offset.
    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-theory.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger ratio of Raman Rabi frequency to scattering rate.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction, especially at short
    internuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\ \text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

\begin{figure}
  \includegraphics[width=0.5\textwidth]{imgs/raman_spectroscopy_raman_beampath.pdf}
  \caption{
    Beampath for generating the frequency for Raman transition in the tweezer.
    (Some mirrors and other optics used for alignment are not included.)
    The two ASE filters before and after the fibers are also shown.
    The red beam path is the $0$-th order of the double pass~(DP) AOM
    which is used for the tweezer.
    When the double-pass~(DP) AOM is turned on, some power is redirected to the first order
    (blue beam path) which generates the required frequency different to drive
    the Raman transition. The two frequencies are recombined on the DP AOM.
    The $0$-th order light is shifted by another single pass~(SP) AOM
    running on a different frequency before recombining.
    Without this AOM, the leak light from the DP AOM will be at the same frequency
    as the $0$-th order light which can cause a significant power fluctuation
    due to interference.
    The experiment typically start with the SP AOM on and the DP AOM off.
    When driving the Raman transition, the powers on both AOMs are ramped simultaneously
    to achieve the desired power at both frequencies.
    \label{f-beampath}
  }
\end{figure}

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-raman.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse-time scan on resonance.
    A decaying Rabi oscillation can be observed, proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$,
    which defines the location of the atoms and molecule.
    We use a bias magnetic field $B_0=8.83(2)~\mathrm{G}$ along the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experience predominantly $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_\textrm{tweezer}^{2.58}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance scales as $P$
    and follows $1/\Delta$ with an offset, where $ P$ is the power in the tweezer.
    The fit also includes a small term that is proportional to $P^2$
    which is caused by the effective magnetic field generated by the tweezer, which is perpendicular to the real magnetic field.
    (b) Raman Rabi frequency ($\Omega_R$) scales as $P^{1.29}$
    and follows $1/\Delta$ with an offset.
    (c) Tweezer power dependency of light shift (up) and Raman Rabi frequency (down)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}
